%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Hi, All
%   Arun Xavier, VAST Thrissur
%
%   for more  Visit my Page - http://arunxeee.blogspot.in/
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%
\chapter*{\centering Acknowledgement}
%


\par
\hspace{0.9cm}During the course of my main project work several persons collaborated directly and indirectly with me. Without their support it would be impossible for me to finish my work. That is why I wish to dedicate this section to recognize their support.
\vspace {.2cm}
\par
\hspace{.35cm}I want to start expressing my thanks to my project guide {\bf \vguide}, \vguidedg\ Dept. of \vdept, because of his valuable advice and guidance towards this work. I received motivation, encouragement and hold up from his during the course of work.

\vspace{.2cm}
\par 
\hspace{.35cm}I am thankful to {\bf \vhod}, 
Head of \vdept\  Department, and our Principal {\bf \vprincipal}, for their sole co-operation.

\vspace{0.2cm}
\par
\hspace{0.35cm}I am grateful to express my thanks to all the faculty members of our mechanical department for their support. I articulate my gratitude to all my friends  for their support and help for this work.


\vspace{0.2cm}
\par
\hspace{0.35cm}Last, but not the least I wish to express my gratitude to God Almighty for His abundant blessings without which this effort would not have been successful.\\[.3 cm]



\begin{flushright}
JISHNU JAYARAJ 
\vclass\  (\vadmissionyear\  Admissions)\\
Govt Engineering College \\
Palakkad - 679 513.
\end{flushright}